\documentclass[10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\pdfgentounicode=1
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}
\setlist[itemize]{leftmargin=*,noitemsep,topsep=0pt}
 
\begin{document}
 
{\LARGE \textbf{Farhan Yuda Pahlevi}}
 
farhan.y.pahlevi@gmail.com | pahlevikun.id | github.com/pahlevikun | linkedin.com/in/pahlevikun | Bogor, West Java, Indonesia (open to remote)
 
\section*{Summary}
Senior Software Engineer bridging mobile and backend to ship production-grade, scalable, high-performance systems serving millions. 8+ years at GoTo Group owning GoFood Merchant authentication and identity, Onboarding Registration, Merchants Payment, and Merchant Data end-to-end --- Kotlin Android, Flutter, Go/Ruby/Elixir/Python microservices, cloud-native. Reduced access-control implementation time by 40\% via ABAC framework; maintained 99.9\%+ availability through L4--L5 incident command; delivered zero-downtime migrations at scale; contributed to IDR 20B/year in revenue growth.
 
\section*{Skills}
\begin{itemize}
\item \textbf{Mobile}: Kotlin, Java, Swift, Dart (Flutter), KMP, Android SDK, Jetpack
\item \textbf{Backend}: Go, Ruby (and Rails), Elixir, TypeScript, Python, PHP (Laravel), Rust (learning)
\item \textbf{Databases}: PostgreSQL, MySQL, Redis, Elasticsearch, SQLite
\item \textbf{Infrastructure}: Kubernetes, Docker, GCP, Tencent Cloud, AWS, New Relic, Grafana, Firebase
\item \textbf{Practices}: ABAC/RBAC, System Design, Zero-downtime deployment, L4--L5 Incident Response, ADR/RFC
\item \textbf{Leadership}: Technical Decisions, Project Time Management, Engineering Mentorship, Domain Anchor and Advisory, Cross-functional Collaboration
\end{itemize}
 
\section*{Work Experience}
\textbf{Senior Software Engineer, Fullstack (Mobile \& Backend) --- GoFood Merchant, Gojek ODS | GoTo Group | Jakarta, Indonesia (Mar. 2023 -- Present)}
\begin{itemize}
\item Cut access-control policy implementation time by 40\% by architecting a production ABAC framework (v1 \& v2) across Go, Ruby, Elixir, and TypeScript microservices, replacing legacy RBAC platform-wide.
\item Achieved 99.9\%+ availability leading zero-downtime cloud-native migration of identity services to Skynet/Tencent; commanded all L4--L5 incidents.
\item Improved more than IDR 20B per year in revenue by implementing new accounting logic.
\item Shipped 5+ features in Kotlin, Go \& Elixir for millions of merchants: Login Redesign, Email OTP, 1-tap on Payment Devices, ABAC integration, and User Re-KYC.
\item Hardened security via PII Encryption and Virtual Group management across a six-language stack with Elasticsearch \& Redis at scale.
\end{itemize}
 
\textbf{Acting Interim Technical Lead --- Merchant Platform, Gojek ODS | GoTo Group | Jakarta, Indonesia (Aug. 2024 -- Jul. 2025)}
\begin{itemize}
\item Delivered Special User Roles with zero-downtime deployment and infrastructure migration as the domain's most senior engineer during critical organisational restructuring.
\item Produced RFCs, ADRs, and runbooks adopted as team templates; drove ABAC adoption across 3+ services, sustaining the 40\% implementation-time reduction.
\item Mentored 5+ engineers on brand user management and scope/tag migration, maintaining team velocity through leadership transition.
\end{itemize}
 
\textbf{Senior Mobile Engineer --- Merchant Platform, GoTo Holdco | GoTo Group | Jakarta, Indonesia (Jan. 2023 -- Aug. 2024)}
\begin{itemize}
\item Launched GoBiz Login Page Redesign (Email OTP phase 1) for millions of merchants; established the design language adopted across all subsequent auth features.
\end{itemize}
 
\textbf{Senior Android Engineer --- GoMerchants, GoTo Financial | GoTo Group | Greater Jakarta Area, Indonesia (Jul. 2018 -- Jan. 2023)}
\begin{itemize}
\item Built and scaled GoBiz Android over 4.5 years for millions of merchants --- owning auth flows, Login SDK, and the ABAC groundwork later deployed platform-wide.
\item Improved performance on high-traffic auth paths via CPU profiling; SDK integrations became the foundation for all subsequent identity features.
\end{itemize}
 
\textbf{Junior Android Developer --- Midtrans | GoTo Group | Greater Jakarta Area, Indonesia (Jun. 2018 -- Jan. 2019)}
\begin{itemize}
\item Rebuilt Midtrans Android SDK from scratch; published GoMerchants AAR, enabling seamless Gojek consumer-app integration across Indonesia's merchant ecosystem.
\end{itemize}
 
\section*{Certifications}
\begin{itemize}
\item Flutter - Beginners Course
\item Facilitator Indonesia Android Kejar 2.0
\item MTA 98-361: Software Development Fundamentals
\item Associate Android Developer
\item Indonesia Android Academy
\end{itemize}
 
\section*{Honors \& Awards}
\begin{itemize}
\item Depok ICT Award (2016)
\item KURMA (2016)
\end{itemize}
 
\section*{Languages}
\begin{itemize}
\item Indonesian (Native or Bilingual)
\item English (Full Professional)
\item Japanese (Elementary)
\item French (Elementary)
\end{itemize}
 
\section*{Education}
\textbf{Bachelor of Engineering -- Informatics Engineering | Universitas Gunadarma | Depok, West Java, Indonesia (2013 -- 2017)}
\begin{itemize}
\item AR hologram Android app as undergraduate thesis; facilitated Google Developer Group programs (Android Kejar, Android Academy), training student cohorts.
\end{itemize}
 
\textbf{Nanodegree -- Associate Android Developer | Udacity (with Google Scholarship) | Online (2017)}
\begin{itemize}
\item Selected as Indonesia scholarship recipient; earned Google Certified Associate Android Developer on completion.
\end{itemize}
 
\end{document}
