\documentclass[10pt]{article}
\usepackage[top=0.3in, bottom=0.3in, left=0.5in, right=0.5in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{titlesec}
\titleformat{\section}{\bfseries}{}{0em}{}
\titlespacing*{\section}{0pt}{5pt}{2pt}
\pdfgentounicode=1
\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1pt}
\setlist[itemize]{leftmargin=*,noitemsep,topsep=0pt}

\begin{document}

{\LARGE \textbf{Farhan Yuda Pahlevi}}

\smallskip
farhan.y.pahlevi@gmail.com $|$ pahlevikun.id $|$ github.com/pahlevikun $|$ linkedin.com/in/pahlevikun

\vspace{2pt}\hrule height 0.5pt\vspace{3pt}

\section*{Professional Summary}
Senior Fullstack Software Engineer with 8+ years delivering production-grade mobile, web, and backend systems at GoTo Group, Indonesia's largest super-app, serving millions of merchants across Southeast Asia. Expert in Kotlin, Flutter, Kotlin Multiplatform (KMP), HTML5, CSS3, JavaScript, React, Next.js (SSR/CSR), and polyglot backend engineering across Go, Ruby on Rails, Elixir, and Python. Deep proficiency in distributed systems design: Redis caching, event-driven microservices, ABAC/RBAC identity systems, OAuth 2.0 token authorisation, and zero-downtime cloud migrations on GCP, AWS, Tencent Cloud, Firebase, and Supabase. Proven technical lead and L4--L5 incident commander: reducing implementation time by 40\%, maintaining 99.9\%+ availability, unlocking IDR 20B+/year in revenue growth, and placing 1st at GoTo Hackathon 2024. Actively integrates LLM-powered AI workflows to accelerate engineering velocity and code quality.

\section*{Technical Skills}

\begin{itemize}
\item \textbf{Mobile}: Kotlin, Java, Android SDK, Jetpack (Compose, ViewModel, LiveData, Room, WorkManager, Navigation, DataStore), Kotlin Multiplatform (KMP), Android Studio, Coroutines/Flow, Dart (Flutter), Swift, Material Design 3, ProGuard/R8, Gradle, Deep Linking, FCM
\item \textbf{Web \& Frontend}: HTML5, CSS3, JavaScript, TypeScript, React, Next.js (CSR/SSR/ISR), Tailwind CSS, Responsive Web Design, SPA/MPA Architecture, Webpack, Vite, REST \& GraphQL API Integration
\item \textbf{Backend}: Go, Ruby on Rails, Elixir (Phoenix), TypeScript (Node.js), Express.js, Python (FastAPI/Django), PHP (Laravel), Rust (learning); REST, gRPC, GraphQL API design
\item \textbf{System Design \& Architecture}: Distributed Caching (Redis), Message Queues (Kafka, RabbitMQ), Pub/Sub, Microservices, Event-Driven Architecture, CQRS, Rate Limiting, API Gateway, Circuit Breaker, Load Balancing, Zero-Downtime Deployment, High-Availability Design
\item \textbf{Databases}: PostgreSQL, MySQL, Redis (caching, session management, pub/sub), Elasticsearch, SQLite, MongoDB; query optimisation, indexing strategy, large-scale schema migration
\item \textbf{Cloud \& Services}: GCP, AWS, Tencent Cloud (Skynet), Firebase (Auth, Firestore, Remote Config), Supabase, Kubernetes, Docker, GitHub Actions, GitLab CI, New Relic, Grafana, Sentry, Helm, CI/CD
\item \textbf{AI \& Optimisation}: LLM integration (OpenAI, Anthropic APIs), GenAI-powered feature development, Prompt Engineering, AI-assisted SDLC, AI workflow optimisation, GitHub Copilot
\item \textbf{Security \& Identity}: ABAC/RBAC, PII Encryption, OAuth 2.0, Token Authorisation (JWT, OIDC), OTP/MFA, Identity \& Access Management (IAM), SSL/TLS, API Security, Virtual Group management
\item \textbf{Engineering Practices \& Quality}: System Design, ADR/RFC, L4--L5 Incident Command, Performance Profiling (CPU/memory), TDD, JUnit, Espresso, Flutter Test, Jest, Unit/Integration/UI Testing, Swagger/OpenAPI, Code Review, Git, GitHub, GitLab, Agile/Scrum, Observability
\item \textbf{Leadership}: Technical Decision-Making, Engineering Mentorship, Cross-functional Collaboration, Domain Anchor \& Advisory, Project Planning \& Delivery
\end{itemize}

\section*{Work Experience}

\textbf{Senior Software Engineer, Fullstack (Mobile \& Backend) | GoFood Merchant, Gojek ODS, GoTo Group} \hfill \textit{Mar. 2023 -- Present}\\
\textit{Jakarta, Indonesia}
\begin{itemize}
\item Architected and shipped production ABAC authorisation framework (v1 \& v2) across 6+ Go, Ruby on Rails, Elixir, and TypeScript microservices: slashing policy implementation time by 40\%, eliminating legacy RBAC debt platform-wide, and enabling fine-grained access control for millions of merchant identities.
\item Sustained 99.9\%+ availability across merchant identity services by commanding zero-downtime cloud-native migration to Skynet/Tencent Cloud and leading all L4--L5 incident responses, authoring structured runbooks that reduced mean time to resolution (MTTR) for critical production incidents.
\item Engineered merchant payment accounting and transaction reconciliation logic across Elixir and Go microservices, directly unlocking IDR 20B+/year in incremental annual revenue for the GoFood merchant ecosystem.
\item Developed merchant-facing web application features using React and Next.js (SSR/CSR), implementing OAuth 2.0 token authorisation, JWT session management, and Firebase real-time integrations to deliver a responsive, production-grade web portal serving millions of GoFood merchants.
\item Delivered 5+ high-impact features end-to-end across Kotlin Android, Go, and Elixir for millions of GoFood merchants: Login Redesign, Email OTP, 1-tap Payment Device auth, ABAC integration, and User Re-KYC, each deployed with zero-downtime rollout strategies.
\item Engineered distributed Redis cache-aside layer across Go, Ruby on Rails, and Elixir authentication services, intercepting high-frequency identity resolution queries for millions of concurrent merchant sessions and significantly reducing PostgreSQL read throughput and p99 latency on critical auth paths.
\item Pioneered AI-assisted engineering adoption across the squad: deploying GitHub Copilot, LLM-powered code review automation, and prompt-engineered test scaffolding to accelerate feature delivery, cut boilerplate authoring time, and raise first-pass pull request quality.
\end{itemize}

\vspace{2pt}
\textbf{Acting Interim Technical Lead | Merchant Platform, Gojek ODS, GoTo Group} \hfill \textit{Aug. 2024 -- Mar. 2025}\\
\textit{Jakarta, Indonesia}
\begin{itemize}
\item Assumed full technical ownership of the Merchant Platform domain during critical organisational restructuring, delivering the Special User Roles system: access model redesign, zero-downtime rollout, and complete cloud infrastructure migration without service disruption.
\item Reduced cloud infrastructure expenditure by auditing and decommissioning unused Kubernetes workloads, rightsizing container resource allocations across 10+ microservices on GCP and Tencent Cloud, and consolidating overlapping services to eliminate redundant compute spend.
\item Authored 10+ RFCs, ADRs, and incident runbooks adopted as team-wide engineering standards; drove ABAC framework extension across 3+ downstream services, sustaining the 40\% policy-implementation-time reduction at scale.
\item Coached and mentored 5+ engineers across brand user management, scope/tag migration, distributed system design, and Redis caching patterns, preserving full delivery velocity through an extended leadership transition.
\item Elevated team engineering standards through structured code review frameworks, blameless incident postmortems, and weekly knowledge-sharing sessions on distributed observability (New Relic, Grafana) and AI-assisted development workflows.
\end{itemize}

\vspace{2pt}
\textbf{Senior Mobile Engineer | Merchant Platform, GoTo Holdco, GoTo Group} \hfill \textit{Jan. 2023 -- Aug. 2024}\\
\textit{Jakarta, Indonesia}
\begin{itemize}
\item Spearheaded GoBiz Login Page Redesign and Email OTP Phase 1 in Kotlin with Jetpack Compose, rolling out to millions of GoFood merchants and establishing the authentication UI system later standardised across all subsequent login and identity features.
\item Designed and delivered Kotlin Multiplatform (KMP) shared library encapsulating authentication flows, session management, and merchant onboarding business logic: establishing a single codebase consumed by both Android and iOS teams, eliminating duplicate implementations, and accelerating cross-platform rollouts. Led a parallel Flutter proof-of-concept to produce an architecture evaluation framework covering code-sharing ratio, runtime performance, and adoption cost that guided the mobile guild's long-term cross-platform strategy.
\end{itemize}

\vspace{2pt}
\textbf{Senior Android Engineer | GoMerchants, GoTo Financial, GoTo Group} \hfill \textit{Jul. 2018 -- Jan. 2023}\\
\textit{Greater Jakarta Area, Indonesia}
\begin{itemize}
\item Architected and scaled GoBiz Android over 4.5 years in Kotlin and Java, serving millions of GoTo merchants end-to-end: owning authentication flows, Login SDK, onboarding registration, payment integration, and the identity ABAC groundwork later promoted platform-wide across GoTo Group.
\item Identified and eliminated authentication performance bottlenecks through systematic CPU profiling and Kotlin Coroutines-based async refactoring, establishing a performance-optimised SDK baseline that became the architectural foundation for all GoTo identity and merchant payment features.
\item Designed and published a modular Kotlin Login SDK using Jetpack (MVVM, Navigation, Clean Architecture), adopted across 3+ GoTo apps to enable cross-product SSO, reducing new-app authentication integration effort from weeks to days.
\item Led cross-functional system design reviews for Go and Ruby on Rails microservices: defining Redis cache eviction policies, Elasticsearch multi-tenant index design, and API rate-limiting strategies while driving Android architecture decisions (MVVM, Clean Architecture, modular Gradle) and enforcing code quality standards via CI/CD, scaling merchant identity and search to millions of active users.
\end{itemize}

\vspace{2pt}
\textbf{Junior Android Developer | Midtrans, GoTo Group} \hfill \textit{Jun. 2018 -- Jan. 2019}\\
\textit{Greater Jakarta Area, Indonesia}
\begin{itemize}
\item Rebuilt Midtrans Android payment SDK from scratch in Java and Kotlin; engineered and published the GoMerchants AAR library that became the integration bridge between Gojek's consumer app and Indonesia's largest merchant payment processing platform.
\end{itemize}

\section*{Education}

\textbf{Bachelor of Engineering, Informatics Engineering | Universitas Gunadarma} \hfill \textit{2013 -- 2017}\\
\textit{Depok, West Java, Indonesia}
\begin{itemize}
\item Undergraduate thesis: AR hologram Android application using computer vision and marker tracking.
\item Facilitated Google Developer Group programmes (Android Kejar, Android Academy), training student cohorts in mobile and Android development.
\end{itemize}

\vspace{2pt}
\textbf{Nanodegree, Associate Android Developer | Udacity (with Google Scholarship)} \hfill \textit{2017}
\begin{itemize}
\item Selected as Indonesia scholarship recipient; earned Google Certified Associate Android Developer upon completion.
\end{itemize}

\section*{Achievements \& Certifications}
\begin{itemize}
\item \textbf{1st Place, GoTo Hackathon 2024}: Won the company-wide internal hackathon; recognised for technical innovation, rapid prototyping capability, and cross-functional solution delivery.
\item \textbf{Google Certified Associate Android Developer} | Udacity / Google Scholarship (2017)
\item \textbf{L4--L5 Incident Commander}, GoTo Group: led critical production incident response for identity, authentication, and merchant payment services across Indonesia's largest super-app.
\end{itemize}

\end{document}
